\section{Introduction}
\label{sec:intro}

\noteCLAUDE{Context: large-scale convex optimization in machine
learning, and screening as the general technique for reducing its
cost.}
Large-scale convex optimization is central to machine learning, and
its cost is often reduced by screening: before or during optimization,
a screening rule identifies a subset of features or samples that can
be removed without altering the solution, reducing the size of the
problem that must actually be solved.

\noteCLAUDE{Classification, kept brief: screening comes in several
flavors; this paper picks one axis, feature versus sample, and one
level, structural theory rather than the conditions that make a
screening rule preserve the solution.}
Screening methods can be classified along several axes: whether the
reduction is provable or heuristic; how it is scheduled, statically,
dynamically, or sequentially; and what it targets. This paper is
concerned with the last axis, feature screening, which removes
features, versus sample screening, which removes samples, and with the
structural theory underlying both, not with the additional conditions
needed to ensure a screening rule preserves the solution; such
conditions are discussed only as motivation and future work.

\noteCLAUDE{Nature of the two targets, illustrated directly by their
originating models in one sentence, so this does not repeat as a
separate history paragraph later.}
Feature screening acts on the coordinates of the optimization
variable, and sample screening acts on the training points that define
the loss, a distinction already visible in the models where each was
first developed: feature screening in sparse learning models such as
the Lasso, where many features are known in advance to be removable,
and sample screening in kernel methods such as the support vector
machine, where many samples are known in advance to be removable
\citep{elghaoui2010safe,ogawa2014sample}.

\noteCLAUDE{The actual gap: shared reliance on duality, no shared
derivation, and even later work that combines the two paradigms stops
short of a common object. Ends deliberately without comment.}
This shared reliance on convex duality has not translated into a
shared derivation. Feature screening is typically derived from primal
sparsity structures, while sample screening is developed through dual
optimization formulations, so each new screening rule is established
on a case-by-case basis, without a shared mathematical vocabulary
connecting the two paradigms. Later work combined the two into
simultaneous screening rules \citep{shibagaki2016simultaneous}, several
of which are derived through Fenchel--Rockafellar duality
\citep{ndiaye2017gap,yamada2021dynamic,tran2025one}, yet even these
combined approaches derive feature and sample screening separately
before pairing them; none formulates a common mathematical object of
which both are manifestations. They appear to be dual.

\addCLAUDE{Deliberately no explanation after this sentence, so the
question below lands as the reader's own reaction rather than a
pre-empted one. Revisit if this reads as too abrupt once the rest of
the introduction is in place.}

\noteCLAUDE{This is the paper's only research question; nothing later
should read as a second, competing question. Wording chosen because by
this point the answer, duality in the sense of equivariance, is
already implicit in "mathematical sense."}
\begin{center}
\emph{In what mathematical sense are feature screening and sample
screening dual?}
\end{center}

\noteCLAUDE{The paper's one "no, but" move: pre-empts "this was already
known informally" by naming formalization, not discovery, as the
contribution. Appears exactly once, here.}
The goal of this paper is not to argue that feature screening and
sample screening are dual. Rather, it is to formulate this apparent
duality as a precise mathematical statement by revealing its hidden
structure.

This is the paper's only research question. Existing screening methods
are typically derived in a model-specific manner; our goal is not to
derive another screening rule, but to identify the common mathematical
structure underlying these derivations.

\noteCLAUDE{The one sentence a reader should remember, stated before any
framework is introduced.}
We introduce a common representation level on which both paradigms are
expressed as transformations of the same mathematical object, so that
Fenchel duality intertwines feature screening with sample screening.

\noteCLAUDE{Explains why the main insight is not obvious, with no formulas
yet: primal construction vs. dual construction look unrelated.}
This insight is not obvious because the two constructions look, on the
surface, unrelated. Feature screening fixes primal variables at a
candidate value; sample screening replaces loss terms by a
Fenchel--Young identity at a candidate dual point. One acts on primal
variables, the other on dual variables, and a direct comparison
between them is not possible without a common language for both.

\noteCLAUDE{Introduces the paper's one central object, the FR
representation, and its dual.}
Convex optimization problems of the form
\[
    \min_{x\in\mathbb R^n}
    f(Ax)+g(x)+a,
    \qquad
    A\in\mathbb R^{m\times n},
    \qquad
    a\in\mathbb R,
\]
with separable
\(
f(y)=\sum_{j=1}^m f_j(y_j)
\)
and
\(
g(x)=\sum_{i=1}^n g_i(x_i)
\),
are encoded as a single quadruple \(p=(f,g,A,a)\), an FR
representation. Columns of \(A\) are features; rows are samples.

\noteCLAUDE{Restates both screening constructions in the FR language, as
direct assumptions on the representation rather than as properties of
an optimal solution; this is what \emph{Why Is This Difficult?} needs
so the two can be compared at all.}
Feature screening, restated in this language, imposes the assumption
\(x_{\bar I}=z\) for a block \(I\sqcup\bar I=\{1,\ldots,n\}\), which
reduces the problem to
\[
    \min_{x_I}
    f(A_Ix_I+A_{\bar I}z)+g_I(x_I)+a+g_{\bar I}(z).
\]
Sample screening, restated in the same language, imposes the
assumption \(s\in\partial f_{\bar J}(A_{\bar J}x)\) for a block
\(J\sqcup\bar J=\{1,\ldots,m\}\); the Fenchel--Young equality
\(f_{\bar J}(A_{\bar J}x)=\langle s,A_{\bar J}x\rangle-f_{\bar J}^*(s)\)
then reduces the problem to
\[
    \min_x
    f_J(A_Jx)+g(x)+\langle A_{\bar J}^{\top}s,x\rangle+a-f_{\bar J}^*(s).
\]
Within our framework, the dual variables used in sample screening
admit a natural interpretation as fixing supporting slopes via the
Fenchel--Young identity.\footnote{Throughout the introduction we write
the operators \(S^F, S^S, R^F, R^S, T^F, T^S\) without their screening
parameters, for readability.}

\noteCLAUDE{States the decomposition; this is the fact that makes the two
constructions above comparable, not an assumed definition.}
\noteLE{Removed the decomposition statement from the introduction, since I want audience focus on duality, nothing else.}
% Both constructions above are proved, not assumed, to decompose as
% \[
%     S^F=R^F\circ T^F,
%     \qquad
%     S^S=R^S\circ T^S,
% \]
% where \(T^F\), \(T^S\) are translation actions and \(R^F\), \(R^S\) are
% coordinate restrictions. This is what makes the two constructions
% above comparable at all: both are now written in the same two
% primitives.

\noteCLAUDE{The framework is a proof strategy, not a second contribution;
keep this subordinate to the main insight above. Names both duality
laws the proof actually uses, not one.}
To bridge this gap, we introduce a representation framework in which
every screening operator decomposes into translation followed by
restriction. Both primitives are equivariant under Fenchel--Rockafellar
duality, a property we call Translation Duality and Restriction
Duality respectively, and their composition is the algebraic mechanism
connecting the two constructions. The framework exists only to make
the main insight provable rather than assumed; it is a proof strategy,
not a second contribution alongside it.

\noteCLAUDE{The paper's one central theorem, stated once here, not proved;
no other theorem should be introduced in the introduction. Presentation
order is fixed: words, then formula, then plain restatement, then the
diagram last, as interpretation rather than anchor.}
The formulation promised above is the following identity.
\[
    (S^F(p))^*
    =
    S^S(p^*),
\]
where \(S^F\) denotes feature screening, \(S^S\) denotes sample
screening, and \((\cdot)^*\) denotes Fenchel--Rockafellar duality.
Feature screening on the primal representation is exactly sample
screening on the dual representation, which is exactly the commutative
diagram
\[
\begin{array}{ccc}
p & \xrightarrow{S^F} & S^F(p)\\
{\scriptstyle *}\big\downarrow & & \big\downarrow{\scriptstyle *}\\
p^* & \xrightarrow{S^S} & S^S(p^*)
\end{array}
\]

\noteCLAUDE{Names the theorem's significance before any secondary result;
consequences named here, detailed only in Section~\ref{sec:screening}.}
This identity establishes a structural correspondence between the two
screening paradigms. As a consequence, results developed for one
paradigm can be transferred to the other through duality. Intrinsic
complexity reduction and simultaneous screening both follow naturally
from this correspondence: they are what the theorem produces, not
separate reasons to care about it.

\noteCLAUDE{Three contributions, tiered to match the Result Hierarchy: a
framework, the main duality result, and its corollaries. Names both
duality laws, not the retired Fenchel Equivariance name.}
This paper makes three contributions. The first is a representation
framework, comprising translation and restriction together with their
duality laws, Translation Duality and Restriction Duality, introduced
only as the means to prove the second. The second, and central,
contribution is feature--sample duality, the identity
\((S^F(p))^*=S^S(p^*)\) stated above. The third comprises its
consequences, intrinsic complexity reduction and simultaneous
screening, both following from feature--sample duality.

\noteCLAUDE{Narrative only, not a contribution; positions safe screening as
future work built on this structural theory.}
The paper separates the structural theory of screening from the
semantic certificates required for safety. This provides a foundation
for future work on safe screening rules, where one additionally
imposes conditions ensuring that the screened problem preserves the
solution set of the original problem.

\noteCLAUDE{Previews Sections~\ref{sec:operators} and~\ref{sec:screening}
without claiming results they haven't proved yet. Fixes the retired
Fenchel Equivariance name and the banned optimality wording.}
The rest of the paper is organized as follows. Section~\ref{sec:operators}
introduces the primitive translation and restriction operations on
Fenchel--Rockafellar representations and proves Translation Duality and
Restriction Duality. Section~\ref{sec:screening} defines feature
screening and sample screening from direct assumptions on the
representation, immediately states the intrinsic complexity corollary,
proves they decompose as translation followed by restriction, proves
they are Fenchel-dual, the paper's main theorem, and immediately states
the simultaneous screening corollary. The final section discusses how
the framework can be extended toward safe screening rules by adding
suitable safety conditions.
